The Anatomy of a Hit: Statistically Learning from the Best

### 2024-04-04 paper/paper.qmd
updated paper again

---
title: "The Anatomy of a Hit: Statistically Learning from the Best"
subtitle: "Modeling the elements that make up top 10 artists' songs"
author: 
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/valence-modeling."
date: April 18 2024
date-format: long
abstract: "We attempt to do some interesting things with models and music - stay tuned!"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

A canonical way to measure how popular a song may be is through the 'valence' or perceived energy of a song. Though measuring valence has been done at a national and cross-artistic-work level [@dodds2010], there has never been any inquiry into song valence on an individual basis. Though difficult to exactly predict what individual song could be a hit, it is very possible to wean out insight from previously released music to statistically learn the most important elements of a great song.

@@

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

@@

>>>>

---
title: "The Anatomy of a Hit: Statistically Learning from the Best"
subtitle: "Modeling the most impactful elements of the most successful musicians."
author: 
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/valence-modeling."
date: April 18 2024
date-format: long
abstract: "We attempt to do some interesting things with models and music - stay tuned!"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
nocite: |
  @*
---

@@

One way to measure how popular a song is through the 'valence' or perceived energy of a song.[investigate the motivation here]. Measuring valence has been done at a national and cross-artistic-work level [@dodds2010], but I investigate solely song valence on an individual basis. Though difficult to exactly predict what individual song could be a hit, it is very possible to wean out insight from previously released music to statistically learn the most important elements of a great song.

@@

@fig-stanareyouokay-2 is a hat plot. It shows... This suggests...

@@

---

---
